An Open-Source OpenSim Oculomotor Model for Kinematics and Dynamics Simulation

### 2018-07-10 doc/manuscript.tex
upd

A fixation controller was implemented as a custom \texttt{OpenSim} plugin. The
parameters of the controller are: the desired horizontal $\theta_H$ and vertical
$\theta_V$ fixation angles (in degrees), the saccade onset and velocity and the
gains of \gls{pd} tracking controller ($k_p$ and $k_d $). A sigmoid function is
used for generating smooth saccade trajectories

@@

\begin{equation}\label{equ:pd-controller}
  \ddot{\theta}(t) = k_p (\theta_d(t) - \theta(t)) + k_d (\dot{\theta}_d(t) -
  \dot{\theta}(t)) 
\end{equation}

The sign and magnitude of $\ddot{\theta}(t)$ both for the horizontal and
vertical coordinates of the fixation target is used to actuate the corresponding
muscle in order to achieve the desired goal. \autoref{fig:model} presents an
instance of the model during simulation with the corresponding muscles
activated. \autoref{fig:simulated-saccade} depicts the simulated coordinates,
speeds and estimated \gls{em} activations that reproduce the desired saccade
trajectory.

@@

A realistic oculomotor model representing the motility of a normal human eye was
presented and made publicly available. The parameters of the model were
calibrated using available experimental measured data. The model can be used for
kinematics and dynamics analysis or as a tool for obtaining the muscle
activations that generate a desired saccade, using a closed-loop fixation
controller in a \gls{fd} manner. There is of course space for further
improvement, which will enhance the accuracy and the predictability of the
proposed computational knee model. In this study, we didn't attempt to model the
muscle pulleys, which vary as a function of the model coordinates. Finally, the
users should consider validation of the eye model based on the requirements of
the targeted utility of the model and the variables of interests.

@@

\bibliography{mylibrary}
\addcontentsline{toc}{chapter}{Bibliography}

>>>>

A fixation controller was implemented as a custom \texttt{OpenSim} plugin. The
parameters of the controller are: the desired horizontal $\theta_H$ and vertical
$\theta_V$ fixation angles (in degrees), the saccade onset and velocity, and the
gains of \gls{pd} tracking controller ($k_p$, $k_d $). A sigmoid function is
used for generating smooth saccade trajectories

@@

\begin{equation}\label{equ:pd-controller}
  \ddot{\theta}(t) = k_p (\theta_d(t) - \theta(t)) + k_d (\dot{\theta}_d(t) -
  \dot{\theta}(t)).
\end{equation}

The sign and magnitude of $\ddot{\theta}(t)$ both for the horizontal and
vertical coordinates of the fixation target is used to actuate the corresponding
muscles in order to achieve the desired goal. \autoref{fig:model} presents an
instance of the model during simulation with the corresponding muscles
activated. \autoref{fig:simulated-saccade} depicts the simulated coordinates,
speeds and estimated \gls{em} activations that reproduce the desired saccade
trajectory.

@@

A realistic oculomotor model representing the motility of a normal human eye was
presented and made publicly available. The parameters of the model were
calibrated using available experimental measured data. The model can be used for
kinematics and dynamics analysis or as a tool for obtaining the muscle
activations that generate a desired saccade, using a closed-loop fixation
controller in a \gls{fd} manner. There is of course space for further
improvement, which will enhance the accuracy and the predictability of the
proposed computational eye model. In this study, we didn't attempt to model the
muscle pulleys, which vary as a function of the model coordinates. Furthermore,
the users should consider validation of the eye model based on the requirements
of the targeted utility of the model and the variables of interests.

@@

\bibliography*{mylibrary}
\addcontentsline{toc}{chapter}{Bibliography}
